### 2015-07-24 LaTeX/skewnormal.tex
addition of abstract and authors

\begin{document}\linenumbers

\begin{center}
{\Large {\bf A spatial skew-$t$ model for threshold exceedances}}\\
\today
\end{center}

\section{Introduction}\label{s:intro}
In many climatological applications, researchers are interested in learning about the average behavior of different climate variables (e.g. ozone, temperature, rainfall).
Our study is motivated by an air pollution application where the focus is not on the average behavior, but instead the behavior over a fixed threshold determined by government regulation.
More specifically, we consider consider the case of compliance for ozone.
A site is said to be in compliance if the fourth highest daily maximum 8-hour concentration averaged over 3 years does not exceed 75 parts per billion (ppb).

@@

Threshold modeling is popular in the field of extreme value statistics where extreme events are naturally defined in terms of exceedances over a high threshold.
\citet{Davison1990} considered modeling threshold exceedances of univariate time series by the generalized Pareto distribution.
Bivariate threshold models for extreme value distributions were considered by \citet{Ledford1996} who introduced a censored approach that provides a way to deal with different types of exceedances of a bivariate threshold in terms of only one or both components.
These threshold models were extended to spatial models for extremes by \citet{Wadsworth2012} and \citet{Thibaud2013} who fit various models to spatial extremes using a censored pairwise likelihood \citep{Padoan2010} based on the approach of \citet{Ledford1996}.
\citet{Huser2014} further extended this to spate-time modeling.
\citet{Engelke2014}, \citet{Wadsworth2014}, and \citet{Thibaud2013a} introduced more efficient inference for threshold exceedances of extremal spatial processes with full likelihood methods.
The previous approaches to threshold modeling are motivated by extreme value theory and assume the threshold is high enough to assume extremal models are valid for the data, and for extrapolation beyond the range of observed values.
Moreover, these approaches are computationally intensive and limited to rather small datasets.
Our application with ozone data does not fit into this framework because we do not focus on exceedances of a very high threshold, but on exceedances of a fixed threshold.

@@

The paper is organized as follows.
Section \ref{s:spatialskew} is a brief review of the spatial skew-$t$ process.
In Section \ref{s:temporal}, we build upon the traditional skew-$t$ by incorporating censoring to focus on tails, partitioning to remove long-range asymptotic dependence, and extending the model to space-time data.
The computing is described in Section \ref{s:comp}.
In Section \ref{s:simstudy}, we present a simulation study that examines the predictive capabilities of this model compared with a na{\"i}ve Gaussian method.
We then compare our method to Gaussian and max-stable methods with a data analysis of ozone measurements from throughout the US in section \ref{s:analysis}.
The final section provides brief discussion and direction for future research.

@@

For a finite collection of locations $\bs_1, \ldots, \bs_n$, denote the vector of observations $\bY = [Y(\bs_1), \ldots, Y(\bs_n)]^T$.
After marginalizing over both $z$ and $\sigma$,
\begin{align}
  \bY \sim \text{ST}_n(\bX \bbeta, \bOmega, \balpha, 2a), \label{eq:fullmodel}
\end{align}
that is, $\bY$ follows an $n$-dimensional skew-$t$ distribution with location $\bX \bbeta$, correlation matrix $\bOmega$, slant parameters $\balpha$ and degrees of freedom $2a$, where $\bX = [\bX(\bs_1)^T, \ldots, \bX(\bs_n)^T]$, $\bOmega = \bomega \bar{\bOmega} \bomega$, $\bomega = \text{diag}\left(\frac{1}{ \sqrt{ab}}, \ldots, \frac{1}{\sqrt{ab}}\right)$, $\bar{\bOmega} = (\bSigma + \lambda^2 \bOne \bOne^T$), $\balpha = \lambda (1 + \lambda^2 \bOne^T \bSigma^{-1} \bOne)^{-1/2} \bOne^T \bSigma^{-1}$ is a vector of slant parameters, and $\bSigma$ is the positive definite correlation matrix of $[v(\bs_1), \ldots, v(\bs_n)]$.
Although any positive definite correlation function could be used, we choose to use the stationary isotropic \Matern correlation with
\begin{align}
  \text{cor}[v(\bs), v(\bt)] = \gamma I(\bs = \bt) + (1 - \gamma)  \frac{ 1 }{ \Gamma(\nu) 2^{ \nu - 1}} \left( \sqrt{2\nu} \frac{ h }{ \rho } \right)^{\nu} K_{\nu} \left( \sqrt{2\nu} \frac{ h }{ \rho } \right) \label{eq:matern}
\end{align}
where $\rho$ is the spatial range, $\nu$ is the smoothness, $\gamma$ is the proportion of variance accounted for by the spatial variation, $K_\nu$ is a modified Bessel function of the second kind, and $h = || \bs - \bt ||$.
This process is desirable because of its flexible tail that is controlled by the skewness parameter $\lambda$ and degrees of freedom $2a$.
Furthermore, the marginal distributions at each location also follow a univariate skew-$t$ distribution \citep{Azzalini2014}.

@@

\section{Spatiotemporal skew-$t$ model for extremes}\label{s:spatial}
In this section, we propose extensions to the skew-$t$ process to model spatial extremes over a large geographic region by introducing censoring to focus on tail behavior and a random partition to remove long-range asymptotic dependence.
For notational convenice, we introduce the model for a single replication, and then extend this model to the spatiotemporal setting in Section \ref{s:temporal}.

\subsection{Censoring to focus on the tails}
Because one of our goals is to model the dependence of the distribution in the tails of the data, we choose to censor values below threshold.
Let
\beq\label{Yt}
  \widetilde{Y}(\bs) = \left\{ \begin{array}{ll}
      Y(\bs) \quad & \delta(\bs) = 1 \\
      T & \delta(\bs) = 0
  \end{array} \right.
\eeq
be the censored observation at site $\bs$ where $Y(\bs)$ is the uncensored observation, $\delta(\bs) = I[Y(\bs) > T]$, and $T$ is a pre-specified threshold value.
Then, assuming the uncensored data $Y(\bs)$ are observations from a skew-$t$ process, we update values censored below the threshold using standard Bayesian missing data methods as described in Section \ref{s:comp}.

\subsection{Partitioning to remove long-range asymptotic dependence}\label{s:part}
The motivation for the partition is that for a large spatial domain, it may not be reasonable to assume sites that are far apart demonstrate asymptotic dependence.
Modeling different levels of asymptotic dependence was discussed by \citet{Wadsworth2012} with a hybrid spatial dependence model.
\citet{Huser2014} also allow for asymptotic dependence across both space and time with a partition structure represented by random discs moving across the space for a random duration with a random velocity and random radius.
We handle the problem of long-range asymptotic dependence with a random partition.
As discussed in Section \ref{s:spatialskew}, the source of long-range dependence is the shared $z$ and $\sigma$.
Therefore, to alleviate this dependence, we allow $z$ and $\sigma$ to vary by site.
The model becomes
\begin{align} \label{eq:partition}
  Y(\bs) &= \bX(\bs)^T \bbeta + \lambda \sigma(\bs) |z(\bs)| + \sigma(\bs) v(\bs).
\end{align}
Let $\bw = (w_1, w_2)$ be the location of a spatial knot.
To model spatial variation, consider a set of spatial knots $\bw_1, \ldots, \bw_K$ from a homogeneous Poisson process with intensity $\mu$ over spatial domain $\calD \in \calR^2$.
The knots define a random partition of $\calD$ by subregions $P_{1}, \ldots, P_{K}$ defined as
\begin{align} \label{eq:subregions}
  P_{k} = \{ \bs : k = \argmin_\ell || \bs - \bw_{\ell} || \}.
\end{align}
All $z(\bs)$ and $\sigma(\bs)$ for sites in subregion $k$ are assigned common values
\begin{align}
  z(\bs) = z_{k} \quad \text{and} \quad \sigma(\bs) = \sigma_{k} \label{eq:sitezsig}
\end{align}
and the $z_k$ and $\sigma^2_k$ are distributed as $z_k \iid N(0, 1)$ and $\sigma^2 \iid$ IG$(a, b)$ where IG is the distribution function of an inverse gamma random variable.
So, within each partition, $Y(\bs)$ follows the spatial skew-$t$ process defined in Section \ref{s:spatialskew}.
Across partitions, the $Y(\bs)$ remain correlated via the correlation function for $v(\bs)$ because $v(\bs)$ spans all partitions.

When incorporating the random partition, conditional on knots $\bw_1, \ldots, \bw_K$, the $\chi$ statistic for two sites $\bs$ and $\bt$ in partitions $k_s$ and $k_t$ respectively is
\begin{align}
  \chi(h) &= I(k_s = k_t) \chi_{\text{skew-}t}(h) + I(k_s \neq k_t) \chi_{\text{Gaus}}(h) \nonumber \\
         &= I(k_s = k_t) \chi_{\text{skew-}t}(h)
\end{align}
where $I(\cdot)$ is an indicator function, $\chi_{\text{skew-}t}(h)$ is the $\chi$ statistic for a skew-$t$ process given in (\ref{eq:chiskew-t}), $\chi_{\text{Gaus}}(h)$ is the $\chi$ statistic for a Gaussian process, and $h = ||\bs - \bt||$.
Therefore, sites in different subregions are asymptotically independent because $\chi_{\text{Gaus}}(h) = 0$ for all $h$.
Marginally, over the knots $\bw_1, \ldots, \bw_K$, $\chi(h) = \pi(h) \chi_{\text{skew}-t}(h)$, where $\pi(h) = \Pr(k_s = k_t)$ is the probability that two sites separated by distance $h$ are in the same partition.
So, to show that $\lim_{h \rightarrow \infty} \chi(h) = 0$, we need only know that $\lim_{h \rightarrow \infty} \pi(h) = 0$. A proof of this is given in Appendix \ref{a:proofsamepartition}.

@@

\subsection{Extension to space-time data} \label{s:temporal}
When using daily measurements, the assumption of temporal independence is often inappropriate.
In this section, we extend (\ref{eq:partition}) to the spatiotemporal setting.
There are several places where temporal dependence could be incorporated in the model, including the residuals $v_t(\bs)$.
However, we choose to allow for temporal dependence in the $\bw$, $z$, and $\sigma$ terms because these terms dictate the tail behavior which is our primary focus.
Let
\begin{align} \label{eq:spatiotemp}
  Y_t(\bs) = \bX_t(\bs)^T \bbeta + \lambda \sigma_t(\bs) |z_t(\bs)| + \sigma_t(\bs) v_t(\bs),
\end{align}
where $t \in \{1, \ldots, T\}$ denotes the day of each observation.
Let \hbox{$\bw_{tk} = (w_{tk1}, w_{tk2})$} be a spatial knot on day $t$, and let $w_{t1}, \ldots, w_{tK}$ be a collection of spatial knots on day $t$.
As in Section \ref{s:part}, these knots define a daily partition $P_{t1}, \ldots, P_{tK}$, and for $\bs \in P_{tk}$,
\begin{align}
  z_t(\bs) = z_{tk}\quad \text{and} \quad \sigma_{t}(\bs) = \sigma_{tk}.
\end{align}
We allow the partition structure to vary from day to day in order to account for sharp spikes in ozone that may not be present every day (e.g. a forest fire).

We use an AR(1) time series model for $w_{tk}$, $z_{tk}$, and $\sigma_{tk}$.
The time series model must be specified after a transformation to preserve the skew-$t$ process at each time point.
For each time-varying parameter, we transform to obtain a standard normal marginal distribution, place a Gaussian prior with autocorrelation on the transformed parameter, and then transform back to obtain the marginal distribution required to preserve the skew-$t$ process.
We first transform the spatial knots from $\calD$ to $\calR^2$ as follows.
Let
\begin{align}
  w^*_{tki} = \Phi^{-1}\left[ \frac{ w_{tki} - \min(\bs_i)}{ \max(\bs_i) - \min(\bs_i) } \right], \quad i = 1, 2
\end{align}
where $\Phi$ is a univariate standard normal density function, and $\bs_i = [s_{1i}, \ldots, s_{ni}]$.
Then the transformed knots $\bw^*_{tk} \in \calR^2$.
We use a copula on $\sigma^2_t(\bs)$ to ensure that the marginal distributions of $\sigma^2_t(\bs)$ are inverse gamma.
Let
\begin{align}
  \sigma^{2*}_t(\bs) =\Phi^{-1}\left\{ \text{IG}[\sigma^2_t(\bs)] \right\}
\end{align}
where IG is defined as before.
We also use a copula on $z_{t}(\bs)$ to ensure that the marginal distributions of $z_t(\bs)$ are half-normal.
Let
\begin{align}
  z^*_t(\bs) = \Phi^{-1}\left\{ \text{HN}[z_t(\bs)] \right\}
\end{align}
where HN is the distribution function of a half-normal random variable.
The AR(1) process for each tail parameter is $\bw^*_{1k} \sim N_w(0, 1)$, $z^*_{1k} \sim N(0, \sigma^2_{1k})$, $\sigma^{2*}_{1k} \sim N(0, 1)$, and for $t > 1$ the time series is modeled as
\begin{align}
  \bw^*_{tk} | \bw^*_{t-1, k} &\sim N_2\left[\phi_w \bw^*_{t-1, k}, (1 - \phi_w^2) \right] \\
  z^*_{tk} | z^*_{t-1, k} &\sim N \left[\phi_z z^*_{t-1, k}, \sigma^2_{tk} (1 - \phi_z^2)\right] \\
  \sigma^{2*}_{tk} | \sigma^{2*}_{t-1, k} &\sim N \left[\phi_\sigma \sigma^{2*}_{t-1, k}, (1 - \phi_\sigma^2) \right]
\end{align}
where $|\phi_w|$, $|\phi_z|$, $|\phi_\sigma| < 1$.
These are stationary time series models with marginal distributions \hbox{$\bw^*_{k} \sim N_2(0, 1)$}, \hbox{$z^*_{k} \sim N(0, \sigma^2_{k})$}, and \hbox{$\sigma^{2*}_{k} \sim N(0, 1)$}.
After transformation back to the original space, $\bw_{tk} \sim \text{Unif}(\calD)$, $z_{tk} \sim HN(0, \sigma^2_{tk})$ $\sigma^2_{tk} \sim \text{IG}(a, b)$.
For each day, the model is identical to the spatial-only model in (\ref{eq:partition}) by construction.

@@

\subsection{Cross validation}\label{s:modelselect}
Models were compared using cross validation with 100 sites used as training sites and 44 sites witheld for testing.
The model was fit using the training set, and predictions were generated at the testing site locations.
Because one of the primary goals of this model is to predict exceedances over a fixed threshold, we use Brier scores to select the model that best fits the data \citep{Gneiting2007}.
The Brier score for predicting exceedance of a threshold $c$ is given by $[e(c) - P(c)]^2$ where $e(c) = I[y>c]$ is an indicator function indicating that a test set value, $y$, has exceeded the threshold, $c$, and $P(c)$ is the predicted probability of exceeding $c$.
We average the Brier scores over all test sites and days.
For the Brier score, a lower score indicates a better fit.

@@

A plot of the relative Brier scores is given in Figure \ref{fig:simbrierscores}.
We find that when the data are generated from a Gaussian process, our method performs comparably to a Gaussian approach.
In general, when the underlying process is not Gaussian, our method results in an improvement over both the max-stable and Gaussian methods.
One exception to this is the case when the generative process is max-stable.
In this case, the max-stable method outperforms our method; however, for predictions further out in the tail, the differences between the max-stable method and our method diminish.
The non-thresholded methods tend to outperform the thresholded methods, but this is not surprising given that in most cases, the data are generated directly from the model used in the method.
% Finally, for setting 5, although the thresholded version of the single-partition model tends to perform the best across all of the extreme quantiles, the difference between the thresholded and non-thresholded methods is no longer significant in the more extreme quantiles.
In summary, our method provides more flexibility for data that demonstrate some level of asymmetry or heavy tails, while still performing comparably to Gaussian methods when the data are symmetric and have light tails.

@@

Standard exploratory data analysis techniques for extremal dependence are very challenging with only 31 days worth of data because it is difficult to estimate extreme quantiles at each site to obtain empirical estimates of $\chi$.
Despite the fact that there is only one month of data, we can get some sense of extremal dependence between sites by looking at joint occurences of high sample quantiles.
Figure \ref{fig:bivariateozone} suggests suggests there is more agreement between sites that are close to one another than sites that are far from one another.
\begin{figure}
  \label{fig:bivariateozone}
  \centering
  \includegraphics[width=\linewidth]{plots/daily-quantiles-ozone.pdf}
  \caption{Daily quantiles for sites that are close (left) and far apart (right)}
\end{figure}

@@

\subsection{Model comparisons}
We fit the model using Gaussian and skew-$t$ marginal distributions with $K=1, 5, 6, 7, 8, 9, 10, 15$ partitions.
We choose to censor $Y(\bs)$ at $T =$ 0, 50 (0.42 sample quantile), and 75 (0.92 sample quantile) ppb in order to compare results from no, moderate, and high censoring.
The upper threshold of 75 ppb was used because the current air quality standard is based on exceedance of 75 ppb.
As with the simuliation study, for models with a threshold of $T = 75$, we use a symmetric-$t$ marginal distribution.
We also compare models with no time series to models that include the time series.
Finally, as a comparison to max-stable methods, we fit the model using the hierarchical max-stable model of \citet{Reich2012} with the data thresholded at $T = 75$.
All methods assume the mean function given in (\ref{eq:datamean}).
To ensure that the max-stable method runs in a reasonable amount of time, we take a stratified sample of the sites to get 800 sites and consider this our new dataset.
We conduct two-fold cross validation using 400 training sites and 400 validation sites as described in Section \ref{s:modelselect}

>>>>

\begin{document}\linenumbers
\begin{center}
{\Large {\bf A spatial skew-$t$ model for threshold exceedances}}\\

{\large Samuel A Morris\footnote[1]{North Carolina State University}, Brian J Reich\footnotemark[1]{}, Emeric Thibaud\footnote[2]{Colorado State University}, and Dan Cooley\footnotemark[2]{}}

\today
\end{center}

\begin{abstract}
\singlespacing
To assess the compliance of air quality regulations, the Environmental Protection Agency (EPA) must know if a site exceeds a pre-specified threshold.
In the case of ozone, the threshold for compliance is fixed at 75 parts per billion, which is high, but not extreme at all locations.
We present a new method based on the spatial skew-$t$ process.
Our method incorporates a random partition to permit long-distance asymptotic independence while allowing for sites that are near one another to be asymptotically dependent, and we incorporate thresholding to allow the tails of the data to speak for themselves.
We also introduce a transformed AR(1) time-series to allow for temporal dependence.
Finally, our model allows for high-dimensional Bayesian inference that is comparable in speed to traditional geostatistical methods for large datasets.
We apply our method to an ozone analysis for July 2005, and find that our model does demonstrate some improvement over both Gaussian and max-stable methods in terms of predicting exceedances over a fixed threshold.

{\bf Key words}: Skew-$t$, random partition,
\end{abstract}

\newpage
\section{Introduction}\label{s:intro}
In many climatological applications, researchers are interested in learning about the average behavior of different climate variables (e.g. ozone, temperature, rainfall).
Our study is motivated by an air pollution application where the focus is not on the average behavior, but instead the behavior over a fixed threshold determined by government regulation.
More specifically, we consider consider the case of compliance for ozone.
A site is said to be in compliance if the fourth highest daily maximum 8-hour concentration averaged over 3 years does not exceed 75 parts per billion (ppb).

@@

Threshold modeling is popular in the field of extreme value statistics where extreme events are naturally defined in terms of exceedances over a high threshold.
\citet{Davison1990} considered modeling threshold exceedances of univariate time series by the generalized Pareto distribution.
Bivariate threshold models for extreme value distributions were considered by \citet{Ledford1996} who introduced a censored approach that provides a way to deal with different types of exceedances of a bivariate threshold in terms of only one or both components.
These threshold models were extended to spatial models for extremes by \citet{Wadsworth2012} and \citet{Thibaud2013} who fit various models to spatial extremes using a censored pairwise likelihood \citep{Padoan2010} based on the approach of \citet{Ledford1996}.
\citet{Huser2014} further extended this to space-time modeling.
\citet{Engelke2014}, \citet{Wadsworth2014}, and \citet{Thibaud2013a} introduced more efficient inference for threshold exceedances of extremal spatial processes with full likelihood methods.
The previous approaches to threshold modeling are motivated by extreme value theory and assume the threshold is high enough that extremal models are valid for the data, and for extrapolation beyond the range of observed values.
Moreover, these approaches are computationally intensive and limited to rather small datasets.
Our application with ozone data does not fit into this framework because we do not focus on exceedances of a very high threshold, but on exceedances of a fixed threshold.

@@

The paper is organized as follows.
Section \ref{s:spatialskew} is a brief review of the spatial skew-$t$ process.
In Section \ref{s:temporal}, we build upon the traditional skew-$t$ by incorporating censoring to focus on tails, partitioning to remove long-range asymptotic dependence, and extending the model to space-time data.
The computing is described in Section \ref{s:comp}.
In Section \ref{s:simstudy}, we present a simulation study that examines the predictive capabilities of this model compared Gaussian amd max-stable methods.
We then compare our method to Gaussian and max-stable methods with a data analysis of ozone measurements from throughout the US in section \ref{s:analysis}.
The final section provides brief discussion and direction for future research.

@@

For a finite collection of locations $\bs_1, \ldots, \bs_n$, denote the vector of observations $\bY = [Y(\bs_1), \ldots, Y(\bs_n)]^T$.
After marginalizing over both $z$ and $\sigma$,
\begin{align}
  \bY \sim \text{ST}_n(\bX \bbeta, \bOmega, \balpha, 2a), \label{eq:fullmodel}
\end{align}
that is, $\bY$ follows an $n$-dimensional skew-$t$ distribution with location $\bX \bbeta$, correlation matrix $\bOmega$, slant parameters $\balpha$ and degrees of freedom $2a$, where $\bX = [\bX(\bs_1)^T, \ldots, \bX(\bs_n)^T]$, $\bOmega = \bomega \bar{\bOmega} \bomega$, $\bomega = \text{diag}\left(\frac{1}{ \sqrt{ab}}, \ldots, \frac{1}{\sqrt{ab}}\right)$, $\bar{\bOmega} = (\bSigma + \lambda^2 \bOne \bOne^T$), $\balpha = \lambda (1 + \lambda^2 \bOne^T \bSigma^{-1} \bOne)^{-1/2} \bOne^T \bSigma^{-1}$, and $\bSigma$ is the positive definite correlation matrix of $[v(\bs_1), \ldots, v(\bs_n)]$.
Although any positive definite correlation function could be used, we choose to use the stationary isotropic \Matern correlation with
\begin{align}
  \text{cor}[v(\bs), v(\bt)] = \gamma I(\bs = \bt) + (1 - \gamma)  \frac{ 1 }{ \Gamma(\nu) 2^{ \nu - 1}} \left( \sqrt{2\nu} \frac{ h }{ \rho } \right)^{\nu} K_{\nu} \left( \sqrt{2\nu} \frac{ h }{ \rho } \right) \label{eq:matern}
\end{align}
where $\rho$ is the spatial range, $\nu$ is the smoothness, $\gamma$ is the proportion of variance accounted for by the spatial variation, $K_\nu$ is a modified Bessel function of the second kind, and $h = || \bs - \bt ||$.
This process is desirable because of its flexible tail that is controlled by the skewness parameter $\lambda$ and degrees of freedom $2a$.
Furthermore, the marginal distributions at each location also follow a univariate skew-$t$ distribution \citep{Azzalini2014}.

@@

\section{Spatiotemporal skew-$t$ model for extremes}\label{s:spatial}
In this section, we propose extensions to the skew-$t$ process to model spatial extremes over a large geographic region by introducing censoring to focus on tail behavior and a random partition to remove long-range asymptotic dependence.
For notational convenience, we introduce the model for a single replication, and then extend this model to the spatiotemporal setting in Section \ref{s:temporal}.

\subsection{Censoring to focus on the tails}
Because one of our goals is to model the dependence of the distribution in the tails of the data, we choose to censor values below a threshold.
Let
\beq\label{Yt}
  \widetilde{Y}(\bs) = \left\{ \begin{array}{ll}
      Y(\bs) \quad & \delta(\bs) = 1 \\
      T & \delta(\bs) = 0
  \end{array} \right.
\eeq
be the censored observation at site $\bs$ where $Y(\bs)$ is the uncensored observation, $\delta(\bs) = I[Y(\bs) > T]$, and $T$ is a pre-specified threshold value.
Then, assuming the uncensored data $Y(\bs)$ are observations from a skew-$t$ process, we update values censored below the threshold using standard Bayesian missing data methods as described in Section \ref{s:comp}.

\subsection{Partitioning to remove long-range asymptotic dependence}\label{s:part}
The motivation for the partition is that for a large spatial domain, it may not be reasonable to assume sites that are far apart demonstrate asymptotic dependence.
Modeling different levels of asymptotic dependence was discussed by \citet{Wadsworth2012} with a hybrid spatial dependence model.
\citet{Huser2014} also allow for varying asymptotic dependence across both space and time with a partition structure represented by random discs moving across the space for a random duration with a random velocity and random radius.
We handle the problem of long-range asymptotic dependence with a random partition.
As discussed in Section \ref{s:spatialskew}, the source of long-range dependence is the shared $z$ and $\sigma$.
Therefore, to alleviate this dependence, we allow $z$ and $\sigma$ to vary by site.
The model becomes
\begin{align} \label{eq:partition}
  Y(\bs) &= \bX(\bs)^T \bbeta + \lambda \sigma(\bs) |z(\bs)| + \sigma(\bs) v(\bs).
\end{align}
Let $\bw = (w_1, w_2)$ be the location of a spatial knot.
To model spatial variation, consider a set of spatial knots $\bw_1, \ldots, \bw_K$ from a homogeneous Poisson process with intensity $\mu$ over spatial domain $\calD \in \calR^2$.
The knots define a random partition of $\calD$ by subregions $P_{1}, \ldots, P_{K}$ defined as
\begin{align} \label{eq:subregions}
  P_{k} = \{ \bs : k = \argmin_\ell || \bs - \bw_{\ell} || \}.
\end{align}
All $z(\bs)$ and $\sigma(\bs)$ for sites in subregion $k$ are assigned common values
\begin{align}
  z(\bs) = z_{k} \quad \text{and} \quad \sigma(\bs) = \sigma_{k} \label{eq:sitezsig}
\end{align}
and the $z_k$ and $\sigma^2_k$ are distributed as $z_k \iid N(0, 1)$ and $\sigma^2 \iid$ IG$(a, b)$ where IG is the distribution function of an inverse gamma random variable.
So, within each partition, $Y(\bs)$ follows the spatial skew-$t$ process defined in Section \ref{s:spatialskew}.
Across partitions, the $Y(\bs)$ remain correlated via the correlation function for $v(\bs)$ because $v(\bs)$ spans all partitions.

When incorporating the random partition, conditional on knots $\bw_1, \ldots, \bw_K$, the $\chi$ statistic for two sites $\bs$ and $\bt$ in partitions $k_s$ and $k_t$ respectively is
\begin{align}
  \chi(h) &= I(k_s = k_t) \chi_{\text{skew-}t}(h) + I(k_s \neq k_t) \chi_{\text{Gaus}}(h) \nonumber \\
         &= I(k_s = k_t) \chi_{\text{skew-}t}(h)
\end{align}
where $I(\cdot)$ is an indicator function, $\chi_{\text{skew-}t}(h)$ is the $\chi$ statistic for a skew-$t$ process given in (\ref{eq:chiskew-t}), $\chi_{\text{Gaus}}(h)$ is the $\chi$ statistic for a Gaussian process, and $h = ||\bs - \bt||$.
Therefore, sites in different subregions are asymptotically independent because $\chi_{\text{Gaus}}(h) = 0$ for all $h$.
Marginally, over the knots, $\chi(h) = \pi(h) \chi_{\text{skew}-t}(h)$, where $\pi(h) = \Pr(k_s = k_t)$ is the probability that two sites separated by distance $h$ are in the same partition.
So, to show that $\lim_{h \rightarrow \infty} \chi(h) = 0$, we need only know that $\lim_{h \rightarrow \infty} \pi(h) = 0$. A proof of this is given in Appendix \ref{a:proofsamepartition}.

@@

\subsection{Extension to space-time data} \label{s:temporal}
When using daily measurements, the assumption of temporal independence is often inappropriate.
In this section, we extend (\ref{eq:partition}) to the spatiotemporal setting.
There are several places where temporal dependence could be incorporated in the model, including the residuals $v_t(\bs)$.
However, we choose to allow for temporal dependence in the $\bw$, $z$, and $\sigma$ terms because these terms dictate the tail behavior which is our primary focus.
Let
\begin{align} \label{eq:spatiotemp}
  Y_t(\bs) = \bX_t(\bs)^T \bbeta + \lambda \sigma_t(\bs) |z_t(\bs)| + \sigma_t(\bs) v_t(\bs),
\end{align}
where $t \in \{1, \ldots, T\}$ denotes the day of each observation.
Let \hbox{$\bw_{tk} = (w_{tk1}, w_{tk2})$} be a spatial knot on day $t$, and let $w_{t1}, \ldots, w_{tK}$ be a collection of spatial knots on day $t$.
As in Section \ref{s:part}, these knots define a daily partition $P_{t1}, \ldots, P_{tK}$, and for $\bs \in P_{tk}$,
\begin{align}
  z_t(\bs) = z_{tk}\quad \text{and} \quad \sigma_{t}(\bs) = \sigma_{tk}.
\end{align}
We allow the partition structure to vary from day to day in order to account for sharp spikes in a response that may not be present every day (e.g. the impact of a forest fire on ozone levels).

We use an AR(1) time series model for $w_{tk}$, $z_{tk}$, and $\sigma_{tk}$.
The time series model must be specified after a transformation to preserve the skew-$t$ process at each time point.
For each time-varying parameter, we transform to obtain a standard normal marginal distribution, place a Gaussian prior with autocorrelation on the transformed parameter, and then transform back to the appropriate marginal distribution for the skew-$t$ process.
We first transform the spatial knots from $\calD$ to $\calR^2$ as follows.
Let
\begin{align}
  w^*_{tki} = \Phi^{-1}\left[ \frac{ w_{tki} - \min(\bs_i)}{ \max(\bs_i) - \min(\bs_i) } \right], \quad i = 1, 2
\end{align}
where $\Phi$ is a univariate standard normal density function, and $\bs_i = [s_{1i}, \ldots, s_{ni}]$.
Then the transformed knots $\bw^*_{tk} \in \calR^2$.
We use a copula on $\sigma^2_t(\bs)$ to ensure that the marginal distributions of $\sigma^2_t(\bs)$ are inverse gamma.
Let
\begin{align}
  \sigma^{2*}_t(\bs) =\Phi^{-1}\left\{ \text{IG}[\sigma^2_t(\bs)] \right\}
\end{align}
where IG is defined as before.
We also use a copula on $z_{t}(\bs)$ to ensure that the marginal distributions of $z_t(\bs)$ are half-normal.
Let
\begin{align}
  z^*_t(\bs) = \Phi^{-1}\left\{ \text{HN}[z_t(\bs)] \right\}
\end{align}
where HN is the distribution function of a half-normal random variable.
The AR(1) process for each tail parameter is $\bw^*_{1k} \sim N_w(0, 1)$, $z^*_{1k} \sim N(0, \sigma^2_{1k})$, $\sigma^{2*}_{1k} \sim N(0, 1)$, and for $t > 1$ the time series is modeled as
\begin{align}
  \bw^*_{tk} | \bw^*_{t-1, k} &\sim N_2\left[\phi_w \bw^*_{t-1, k}, (1 - \phi_w^2) \right] \\
  z^*_{tk} | z^*_{t-1, k} &\sim N \left[\phi_z z^*_{t-1, k}, \sigma^2_{tk} (1 - \phi_z^2)\right] \\
  \sigma^{2*}_{tk} | \sigma^{2*}_{t-1, k} &\sim N \left[\phi_\sigma \sigma^{2*}_{t-1, k}, (1 - \phi_\sigma^2) \right]
\end{align}
where $|\phi_w|$, $|\phi_z|$, $|\phi_\sigma| < 1$.
These are stationary time series models with marginal distributions \hbox{$\bw^*_{k} \sim N_2(0, 1)$}, \hbox{$z^*_{k} \sim N(0, \sigma^2_{k})$}, and \hbox{$\sigma^{2*}_{k} \sim N(0, 1)$}.
After transformation back to the original space, $\bw_{tk} \sim \text{Unif}(\calD)$, $z_{tk} \sim HN(0, \sigma^2_{tk})$ $\sigma^2_{tk} \sim \text{IG}(a, b)$.
For each day, the model is identical to the spatial-only model in (\ref{eq:partition}) by construction.

@@

\subsection{Cross validation}\label{s:modelselect}
Models were compared using cross validation with 100 sites used as training sites and 44 sites withheld for testing.
The model was fit using the training set, and predictions were generated at the testing site locations.
Because one of the primary goals of this model is to predict exceedances over a fixed threshold, we use Brier scores to select the model that best fits the data \citep{Gneiting2007}.
The Brier score for predicting exceedance of a threshold $c$ is given by $[e(c) - P(c)]^2$ where $e(c) = I[y>c]$ is an indicator function indicating that a test set value, $y$, has exceeded the threshold, $c$, and $P(c)$ is the predicted probability of exceeding $c$.
We average the Brier scores over all test sites and days.
For the Brier score, a lower score indicates a better fit.

@@

A plot of the relative Brier scores is given in Figure \ref{fig:simbrierscores}.
We find that when the data are generated from a Gaussian process, our method performs comparably to a Gaussian approach.
In general, when the underlying process is not Gaussian, our method results in an improvement over both the max-stable and Gaussian methods.
One exception to this is the case when the generative process is max-stable.
In this case, the max-stable method outperforms our method; however, for predictions at high quantile levels, the differences between the max-stable method and our method decrease.
The non-thresholded methods tend to outperform the thresholded methods, but this is not surprising given that in most cases, the data are generated directly from the model used in the method.
% Finally, for setting 5, although the thresholded version of the single-partition model tends to perform the best across all of the extreme quantiles, the difference between the thresholded and non-thresholded methods is no longer significant in the more extreme quantiles.
In summary, our method provides more flexibility for data that demonstrate some level of asymmetry or heavy tails, while still performing comparably to Gaussian methods when the data are symmetric and have light tails.

@@

Standard exploratory data analysis techniques for extremal dependence are very challenging with only 31 days worth of data because it is difficult to estimate extreme quantiles at each site to obtain empirical estimates of $\chi$.
Despite the fact that there is only one month of data, we can get some sense of extremal dependence between sites by looking at joint occurrences of high sample quantiles.
For example, Figure \ref{fig:bivariateozone} suggests there is more agreement between sites that are close to one another than sites that are far from one another.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{plots/daily-quantiles-ozone.pdf}
  \caption{Daily quantiles for sites that are close (left) and far apart (right)}
  \label{fig:bivariateozone}
\end{figure}
Another aspect that distinguishes our approach from more traditional extremes analyses, is how the threshold is selected.
Traditionally, a threshold is chosen based on the assumption that beyond the threshold, the data follow an extremal model.
In our example, a threshold of 75 ppb which is $q(0.92)$ for all observations, but marginally it represents anywhere from $q(0.06)$ to $q(1)$.

@@

\subsection{Model comparisons}
We fit the model using Gaussian and skew-$t$ marginal distributions with $K=1, 5, 6, 7, 8, 9, 10, 15$ partitions.
We choose to censor $Y(\bs)$ at $T =$ 0, 50 (0.42 sample quantile), and 75 (0.92 sample quantile) ppb in order to compare results from no, moderate, and high censoring.
The upper threshold of 75 ppb was used because the current air quality standard is based on exceedance of 75 ppb.
As with the simulation study, for models with a threshold of $T = 75$, we use a symmetric-$t$ marginal distribution.
We also compare models with no time series to models that include the time series.
Finally, as a comparison to max-stable methods, we fit the model using the hierarchical max-stable model of \citet{Reich2012} with the data thresholded at $T = 75$.
All methods assume the mean function given in (\ref{eq:datamean}).
To ensure that the max-stable method runs in a reasonable amount of time, we take a stratified sample of 800 sites and consider this our new dataset.
We conduct two-fold cross validation using 400 training sites and 400 validation sites as described in Section \ref{s:modelselect}
